Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-21 latex/article.tex
wip

\subsection{Design principle}

@@

To implement the integration on $B_R(x)\cap\Shape$
(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
digital points inside such domain (Fig.~\ref{fig:approx}-$b$) and then
to estimate the geometrical moment as the sum of the geometrical
moments of each elementary cubes lying in the intersection. On GPU,

\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx1}}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-reg}}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-reg-2}}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-bh}}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-ada}}
  \end{center}
  \caption{BALBLABLABLA.}
  \label{fig:approx}
\end{figure}

>>>>

We first present design principles for the GPU implementation and then
present our approaches.

\subsection{Design principles}

@@

To implement the integration on $B_R(\vx)\cap\Shape$\todo{fix Z vs X}
(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
digital points inside such domain (Fig.~\ref{fig:approx}-$b$) and then
to estimate the geometrical moment as the sum of the geometrical
moments of each elementary cubes lying in the intersection. On GPU,
\emph{mipmap} textures to obtain a multiresolution information: if the
input binary object is stored in a 3D texture, GPU hardware can
construct a multiresolution pyramid such that 8 neighboring voxel
intensities at level $l$ are averaged to define the voxel value at
level $l+1$. If the level 0 corresponds to the binary input object, at
a given level $l$, a voxel $(x,y,z)$ contains the fraction of $Z$
belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
consequence, we can approximate the volume of $B_R(x)\cap\Shape$ by
considering mipmap values at a given resolution $l$
(Fig.~\ref{fig:approx}-$c$). In this case, errors only occurs for
cells lying inside $\Shape$ (with density 1) not entirely covered by
$B_R(\vx)$.
\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-2}}
  \end{center}
  \caption{Integral computation with an area estimation from pixel
    counting $(b)$ or from densities (represented by different
    grayvalues) in a mipmap approximation of $\Shape$.}
  \label{fig:approx}
\end{figure}

Using the hierachical nature of the mipmap texture, we could also
consider hierachical decompisitions of either $B_R(\vx)$
(Fig.~\ref{fig:approx2}-$a$) or $B_R(\vx)\cap\Shape$
(Fig.~\ref{fig:approx2}-$b$). The idea would be to decompose the
regions into mipmap cells of different resolution in order to limit
the number of texture access (important bottleneck on GPU hardwares)
and to get better approximated quantities. Note that for the scenario
in Fig.~\ref{fig:approx2}-$b$, there is no approximation (\wrt the
regular grid case) since  geometrical moments are additive quantities.
\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-bh}}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-ada}}
  \end{center}
  \caption{Adaptive approximation of the integration using a
    hierarchical decomposition of the ball $B_R(\vx)$ $(a)$, or a decomposition of $B_R(\vx)\cap\Shape$.}
  \label{fig:approx2}
\end{figure}
